Cover letter for the original IJRR submission

### 2017-12-12 review_tro_2/reviewer_response.tex

\leavevmode \\
\section{Answers to Reviewer 2}
\quot{All the issues I raised in the first review have been addressed in
the revised version. I'm satisfied with most of the answers and the
changes made to the paper. In particular the novelty of the paper with
respect to the conference works is clarified. I appreciate also the new
structure of the manuscript that integrates material previously
relegated to the Appendices into the main body. Now, this work seems to
be self contained enough for a journal. }
\as{Thanks for the comment. We agree with the reviewer that the paper is better this way.}

\leavevmode \\
\quot{
1. I understand the point of view of the authors who focus on
multi-contact planning and would like to refer only briefly to previous
work in motion planning for multi-legged, statically-stable robots. In
principle that is OK, but I suggest to extend the paragraph added at
the end of Section I.A by few sentences that clarify what are the
advantages of your motion planning system with respect to these older
approaches. You are focusing on humanoids, for which these gains are
pretty obvious, but what about multi-legged robots? As an inspiration I
recommend this youtube video showing a simulated hexapod that does
something similar to your HyQ simulated example
\url{https://www.youtube.com/watch?v=Xio1TbjAK80}}

\as{TODO}
\leavevmode \\

\quot{
While the answer about the environment model is satisfying, I think
that you should no only refer to the FCL library in a footnote, but to
cite the paper that explains how it works.
}
\as{Thanks for the suggestion. The citation has indeed been included, as reference TODO}
\leavevmode \\

\quot{
In Tab. V you refer to the computation time in units - seconds,
minutes and hours. If so, you should be more specific as to the
source(s) of the numbers you give in that table. I understand the fact
that it is practically impossible to have a fair comparison in that
point, and the whole community is working toward changing this
situation (as you explain). But you should write explicitly that you
took the numbers from the respective papers, or from your
re-implementation of the algorithms you consider (I think it is not the
case). Well, the papers [8], [17], [18] are quite old, and comparing
the computation times achieved on the computers available 10 years ago
and nowadays isn't convincing. 
}
\as{Thanks for the comment. Indeed, we did not reimplement the solutions, so we modified the paper to state explicitely that the times indicated are those found in the original papers. Although we agree that the times do not stand as proofs, we still believe that the order of magnitude of the time computations remains significant, because an algorithm that took hours to compute 10 years ago is unlikely to perform in less than a few seconds on a modern computer, especially since our implementation is single threaded, and does not take any advantages of recent advances such as GPU programming. In any case, the reviewer is right when he says that this section should be clarified.
Thus, we removed our over-statement ``\textit{Table V presents the computation times for these scenarios, clearly demonstrating that our approach is order of magnitude faster than previous works}'' and added the following comment in Section VIII E.}
\qt{
Table V presents the computation times for these scenarios. Since no implementation of the previous methods is available, we had no choice but to indicate the times directly taken from their corresponding papers.
In the case of older contributions such as [8], [17], [18], because of the technological progress, it appears that our results would have been more meaningful if the benchmarks were run on a modern computer. However, we believe that the order of magnitudes between the performance of each method remain significant to suggest that our method is faster.
}
\leavevmode \\

### 2017-12-12 body/results.tex
reviewer 2 3 - performance

Table~\ref{tab:compprev} presents the computation times for these scenarios, clearly demonstrating that our approach is order of magnitude faster than previous works.

>>>>

%~ Table~\ref{tab:compprev} presents the computation times for these scenarios, clearly demonstrating that our approach is order of magnitude faster than previous works.
Table~\ref{tab:compprev} presents the computation times for these scenarios. Since no implementation of the previous methods is available, we had no choice but to indicate the times directly taken from their corresponding papers.
In the case of older contributions such as~\cite{Hauser06usingmotion},~\cite{DBLP:conf/iser/EscandeKMG08} and~\cite{Bouyarmane2009}, because of the technological progress, it appears that our results would have been more meaningful if the benchmarks were run on a modern computer. However, we believe that the order of magnitudes between the performance of each method remain significant to suggest that our method is faster.
